He-Man: A domain-specific language for lightweight concurrency

### 2012-03-03 paper/paper.tex
some notes and shit.

@@

\section{The event loop model}

Networking applications require a very constrained form of concurrency. Because
I/O (both network and disk) latency dominates the computation time, each
client's thread of execution spends most of its time waiting on I/O. In
particular, we would like to always yield to a client no longer blocked on I/O;
we need not yield to blocked clients, nor do we need arbitrary interleaving of
execution.

As of version 2.5.44, Linux has supported \t{epoll} for non-blocking
multiplexing I/O. A server can register any number of file descriptors with
\t{epoll\_ctl}, and a call to \t{epoll\_wait} returns the ready descriptors.

>>>>

% Contributions; probably should be elsewhere
We identify our contributions as:
\begin{enumerate}

\item We present a case study of compiled embedded domain specific
  language design and implementation.
\end{enumerate}

@@

\section{The event loop model}
%% XXX: it isn't really clear what's going on in this section; it
%% doesn't /really/ talk about event loop stuff in general. It is
%% talking about one possible way to write event based things (the way
%% He-Man generates).

Networking applications require a very constrained form of
concurrency. Because I/O (both network and disk) latency dominates the
computation time, each client's thread of execution spends most of its
time waiting on I/O. In particular, we would like to always yield to a
client no longer blocked on I/O; we need not yield to blocked clients,
nor do we (usually) need arbitrary interleaving of execution.

%% XXX: do wereally want to talk about this?
As of version 2.5.44, Linux has supported \t{epoll} for non-blocking
multiplexing I/O. A server can register any number of file descriptors with
\t{epoll\_ctl}, and a call to \t{epoll\_wait} returns the ready descriptors.
